% \story{name}{title}{story}{pronouns}{major}{year}{flag commands}
\story{March Renfro}{Realizations and Aftermaths}{
I’m not sure where to really start with this so... let’s go to the very start 
of The Realization. Looking back, I’d say that was early elementary 
school—before I knew what love fully was. I had a friend who always had cold 
hands and during break time we would hold hands. 


“Yours are always so warm!” she’d tell me, and we’d go about our time drawing in
the dirt with sticks. It just so worked out that she was left-handed and I’m 
right-handed, so we could hold hands while we drew. 


At the time I wouldn’t know it, but I had a huge crush on her. This would become
a running theme where I’d fall a little in love with all my friends as the years
went on—boys, girls, non-binary, didn’t matter.


I was twelve when I learned not everyone felt that way. It was actually at a 
sleepover and I made up a fake crush on a guy to avoid telling my friend I liked
her. All the girls were fawning over guys and it dawned on me that I was
different in that regard. I took this knowledge and repressed myself, throwing 
myself so far into the closet because it was a religious school and well... 
2012.


Around this time, I also had another Realization about myself—this one harder 
to accept and harder still to talk about with my family. (To date, only one 
knows this part; if any of my other family members stumbles on this... uh... 
surprise?)


I started to fully accept that maybe, just maybe... I wasn’t cis. It hit off and
on for years—a cycle of self-denial and quiet pondering. There was a point where
I finally accepted I was trans and just decided that I would never come out.
(Spoiler: I lied to myself, thankfully.)


Okay, so at this point I know I’m not straight or even cis for that matter and I
live in the smallest religious area. I’m terrified and now seventeen; a senior 
in high school. 


I decided to come out at least to my closest circle of friends—four people... 
Oh boy, did that end poorly.


One of the people in that group ended up telling our ENTIRE high school, so 
that was great... People didn’t take it well; they told my friends to stop 
hanging out with me, told me I was going to hell, quite a lot of nasty stuff.


It was rough and I repressed the trans part even further into myself; accepting 
that I would just live a lie forever. 


Then I got into Aaniiih Nakoda College. (I would get my associate degree in 
Computer Information Sciences from here!)


During my time at ANC, I had a queer instructor/boss for a while (mentor might 
be the better term; it was a work-study). His husband was also trans and I 
adored them so much. They became my inspiration and are the only reason I 
decided to slowly tell my family I’m trans. (If they find this: Hello! I hope 
things are going great for you; you’re amazing!!)


It is now 2020 and I’m in my third year of Electrical Engineering. I’m out, for 
the most part, and feel great. Currently I’m actively transiting, and it’s been 
fantastic. Of course, there are other stories and anecdotes that I could share; 
but I feel like this is a good start.
}
{\he, \they}{Electrical engineering}{Junior}
{\asexualflagstory \pansexualflagstory \transgenderflagstory}
