% Gay, Bisexual, Transgender, trans man (vaguely nonbinary)
\story{Murdock Orrorin Zephakar Criswell}{Believe Us}
{When I was a wee 14 year old experiencing my sexuality crisis, identifying as x
y and z were just never enough, I always felt kind of alien to myself.

I started using a name online that I liked (it was Elliot, which I've grown out
of) and using he/him pronouns thinking it would just be kinda fun to pretend to
be a boy, and to my surprise, I was actually much more happy with that.

I told my mom in the car on the way home from the library one day, "Hey, I
think I've experienced gender euphoria."

She promptly told me she doesn't think being transgender existed, "that's not
real," she said. It was 2013. And so I didn't mention it again. I started using
my deadname again online and I went back into whatever type of closest I had
built for myself. And it was still not enough, it never felt right.

My mom had historically been really abusive, physically and emotionally, my
whole life. She 'accepted' my sexuality, at the time I identified as bisexual.
She wouldn't let it go, she would always invade my privacy over it, every girl
I had hung out with she pried for information from me, saying she couldn't
understand it; why would I like girls? Like. I don't know? I just do? It was a
pressing issue I had with her over my time in high school.

When I turned 18 I met a guy and admitted I was questioning my gender, and he
accepted that which is great! He's still a friend of mine to this day. We dated
seriously for about 2 years, but our relationship took a left turn suddenly
when I had chosen a name and decided on my pronouns finally. He was still
supportive but, in a more sexual way than I had expected, and didn't really use
the name and pronouns I had asked him to use. He said he hated the name I
chose, that if I was transitioning that I should've told him before, he
would've adjusted back then instead of struggling now.

I told him that wasn't REALLY and excuse to deadname me to his friends who were
using the name I wanted. Really the most support I got from him was when he was
interested in having sex, and it really had an affect on my mental health and
how I view my body in relation to my transition, which I'm still working
through as I progress.

My mom, as I mentioned before, didn't support me and my name change and new
pronouns. She would make fun of me to her friends, deadname me in public after
I had already introduced myself under my new name, and would yell at me at home
if I said anything about it to her. I posted on facebook, just a little vent,
and my uncle (who is also genderqueer) saw it. He hadn't talked to her in
years, but he called her on the phone one day and lectured her about how she
was damaging me. That she was being a bully, the exact opposite of what should
be expected of a mother with a child who is lgbt. He told her it wasn't about
her or how she felt during my transition, that I had already considered her
feelings and that I was just trying to live my best life and in the truest way
I could. She stopped deadnaming me after that, mostly because she just stopped
referring to me altogether. She got worse in other ways though.

I was about 20 when I decided to transition, I had just turned 20 that April,
started HRT on July 11th 2018 at a dose of 100mg/1ml every 2 weeks. I cried
when I got my first shot on the way home. My mom drove me. It was several
months after my uncle had scolded her for her actions. She still didn't get it
She told me I was ruining my body. But man. I didn't care. I was so excited.

In early December 2018, early in the month my mom got into an argument with me
over my therapy diagnosis of PTSD, which she wielded against me about my
transition, saying that my hormones were out of balance and that I was faking
it, that I was lying to my therapist about her and making her seem like an
abuser. She kicked me out after I refused to let her see my laptop, presumably
to snoop on me. And so I left. I moved to Montana. I finished my semester
dropped out, 5 classes before I got my degree, and just left. I stayed with my
uncle for a bit, until December 30th, and then I got as far away as I could
from her. I changed everything, blocked her everywhere, and my uncle actually
filed for adult adoption paperwork so that I would legally be removed from her.

On June 12th 2019 I got my hysterectomy, performed by Dr. Samuel Sillitti at
Bozeman Deaconess hospital. He never misgendered me, he accepted me
wholeheartedly as a transgender man just trying to live my life. One of the
easiest decisions I've ever made. I will forever be grateful to him.

I celebrated my 1 year manniversary by hosting a small gender reveal party (its
a boy!)

On February 4th 2020 I had my top surgery performed by Dr. Emilia Ploplys in 
Great Falls. She's been very helpful, has done these surgeries often, and has
always made me feel at home in my own body. Second easiest decision in my life.

A lot of the time, trans people feel like they should've been born cis, or
should've been happy with their life before they transition. I've never felt
like my body was wrong in that way. Being trans was a part of me this whole
time, and finally being who I was going to be in some way or another is good. I
never felt like I was sacrificing myself for this transition. I knew I would
lose friends, family would disown me, et cetera. But that didn't matter to me.
I needed to matter more to myself than they mattered to me.

Being trans for me is self love, a conscious choice, because I saw how
To anyone questioning, you'll know the right decision when it gets to you. You
will find support everywhere, and you can always change your mind. Your
identity is allowed to be fluid.

To anyone suffering, remember that your life and body are more important than
hateful words and self doubt. You will be who you were meant to be. You will
get there, you will (and must!) learn to love yourself every step of the way.}
{He/Him/His}{Biological Anthropology}{Junior Transfer}
